Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2020-02-27 xrb/paper.tex
Add space between magnetic field values and the G symbol for Gauss in section 6.

In addition to extending our models to 3D and relaxing the
approximations used in this study, in the future we plan to perform a
number of additional further studies.  These include investigating the
effects of ignition latitude and different initial models. We also
plan to model mixed H/He bursts. This will require a different
reaction network, and perhaps different resolution
requirements. A long term goal is to include magnetohydrodynamics in
our models. Although the magnetic fields of neutron stars exhibiting
X-ray bursts are relatively weak, with $B \lesssim 10^8 - 10^9$G
\citep{mukherjee2015magnetic} (at least compared to e.g. magnetars,
which have $B\lesssim 10^{15}$G), it has been found by
\citet{art-2016-cavecchi-etal} that even weak magnetic fields could
have a non-negligible effect on the flame propagation, reducing
confinement due to the Coriolis force and leading to increased flame
speeds. Ultimately, we wish to link our simulations to observed light
curves. To do this, we will need to explore radiation transport in
order to model how the burst energy propagates through the outer
layers of the neutron star atmosphere.

>>>>

In addition to extending our models to 3D and relaxing the
approximations used in this study, in the future we plan to perform a
number of additional further studies.  These include investigating the
effects of ignition latitude and different initial models. We also
plan to model mixed H/He bursts. This will require a different
reaction network, and perhaps different resolution
requirements. A long term goal is to include magnetohydrodynamics in
our models. Although the magnetic fields of neutron stars exhibiting
X-ray bursts are relatively weak, with $B \lesssim 10^8 - 10^9$~G
\citep{mukherjee2015magnetic} (at least compared to e.g. magnetars,
which have $B\lesssim 10^{15}$~G), it has been found by
\citet{art-2016-cavecchi-etal} that even weak magnetic fields could
have a non-negligible effect on the flame propagation, reducing
confinement due to the Coriolis force and leading to increased flame
speeds. Ultimately, we wish to link our simulations to observed light
curves. To do this, we will need to explore radiation transport in
order to model how the burst energy propagates through the outer
layers of the neutron star atmosphere.
